---
title: "Untitled"
author: "Alicia Yang"
date: "9/26/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)
```

```{r load_data, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

##create a ggplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

alternate way of making the plot

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

saving initial plots, mostly don't use this

```{r}
scatterplot = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

scatterplot
```

adding color 

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4)
```

why do 'aes' positions matter?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4) + 
  geom_smooth(se = FALSE)
```

vs

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4) + 
  geom_smooth(se = FALSE)
```

##defined color aesthetic everywhere in plot; color applying everywhere rather than single place
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .4) + 
  geom_smooth(se = FALSE)
```

##creating facets; want names to be in columns

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .4) + 
  geom_smooth(se = FALSE) + 
  facet_grid(~name)
```

##This is fine but not interesting
```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .35) +
  geom_smooth(se = FALSE)
```

##Some extra stuff
##Don't make this plot
```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_smooth(size = 2, se = FALSE)
```

2D density
if don't want to show every single datapoint 

```{r}
#install.packages("hexbin")
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_hex()
```


## More kinds of plots
```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram(position = "dodge")
```

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram() +
  facet_grid(~name)
```

density plots
```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = .3) 
```


boxplot
``{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot(alpha = .3)
```

violinplot
```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_violin()
```


ridge plots!!
```{r}
weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```

##saving a plot

```{r}
ggp_ridge_temp = 
  weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
  
ggsave("ggplot_temp_ridge.pdf", ggp_ridge_temp)
```


##embedding plots in Rmd
#keep in mind how looks w/ fig.width
```{r, fig.width = 12}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .4) + 
  geom_smooth(se = FALSE) 
```



